Metropolitan Areas (Deaths & Case)

### 2020-11-17 KPMG Team/Dashboard/visualization_scripts/msa_county_state_cities.Rmd
figures per pax

# plotting 
library(ggplot2)
library(ggthemes)
library(extrafonts)
# library(hrbrthemes) 
# library(geofacet)

@@

# not much to do
county_sum <- covid %>%
  filter(date == max(covid$date)) # latest

# Preview 
head(county_sum, 50)

@@

@@

@@

@@

ggsave("state-msa-us.png", width = 8, height = 5, dpi = 300)
```

@@

  ggplot(data = county_map_state) +
    geom_sf(aes(fill = cases)) + 
    scale_fill_viridis_c(option = "magma", direction = -1) + 
    labs(title = paste(state_name)) +
    theme_void()

@@

# e.g. 
TX <- county_state_map("Texas")
CA <- county_state_map("California")
FL <- county_state_map("Florida")
MA <- county_state_map("Massachusetts")
# NY <- county_state_map("New York")
NJ <- county_state_map("New Jersey")
IL <- county_state_map("Illinois")
# GA <- county_state_map("Georgia")

@@

plot_grid(TX, CA, FL, IL, MA, NJ, ncol = 3)
```

@@

# ggsave("county-state.png", width = 8, height = 5, dpi = 300)
```
### Metropolitan Cases

>>>>

# plotting 
library(ggplot2)
library(ggthemes)
library(showtext)

showtext_auto()

font_add(family = "raleway", regular = "C:/Users/louis/Dropbox/Stuff/Fonts/Raleway-Regular.ttf")

```{r cache = TRUE}

@@

county_sum_total <- covid %>%
  filter(date == max(covid$date)) # latest

# wave 2 
county_sum_wave_2_start <- covid %>%
  filter(date == "2020-06-15") # %>% # latest

county_sum_w2 <- county_sum_total %>% 
  inner_join(county_sum_wave_2_start, by = c("fips", "county")) %>% 
  mutate(cases = cases.x - cases.y) %>%
  mutate(deaths = deaths.x - deaths.y) %>% 
  rename(start_date = date.y) %>% 
  rename(end_date = date.x) %>%
  select(fips, county, population, start_date, end_date, cases, deaths)

# DATA WITH POPULATION
county_census <-census %>% 
  rename(fips = GEOID) %>% 
  left_join(covid, by = "fips")

county_census_total <- county_census %>% 
  filter(date == "2020-11-14")
# idk why max isn't working

# WAVE 2 
county_census_sum_w2_start <- county_census %>%
  filter(date == "2020-06-15")

county_census_sum_w2 <- county_census_total %>% 
  inner_join(county_census_sum_w2_start, by = c("fips", "county", "population", "state")) %>% 
  mutate(cases = cases.x - cases.y) %>%
  mutate(deaths = deaths.x - deaths.y) %>% 
  rename(start_date = date.y) %>% 
  rename(end_date = date.x) %>%
  select(fips, county, population, start_date, end_date, cases, deaths)

county_census_sum_w2

View(county_census_sum_w2)
dim(county_census_sum_w2)
```

@@

county_geo_w2 <- merge(county_lines, county_sum_w2, by = "fips")
county_map_w2 <- county_geo_w2 %>% st_transform('+proj=longlat +datum=WGS84')

# census county, wave 2
county_census_geo_w2 <- merge(county_lines, county_census_sum_w2, by = "fips") 
county_census_map_w2 <- county_census_geo_w2 %>% st_transform('+proj=longlat +datum=WGS84')

@@

county_map_US_w2 <- county_map_w2 %>% 
  filter(!state %in% outside_mainland)

county_census_map_US_w2 <- county_census_map_w2 %>% 
  filter(!state %in% outside_mainland)

# ---

@@

# --- 
# PLOTS

@@

# save to image function - last plot 
# ggsave("state-msa-us.png", width = 8, height = 5, dpi = 300)
```

@@

  ggplot(data = county_map_state) +
    geom_sf(aes(fill = cases)) + 
    scale_fill_viridis_c(option = "magma", direction = -1) + 
    labs(title = paste(state_name),
         subtitle = "Total Cases") +
    theme_void()

@@

# census

county_pax_cases_w2 <- function(state_name) {

  county_census_map_state <- county_census_map_US_w2 %>% 
    filter(STATEFP == fips_code) %>%
    filter(cases >= 0)

  ggplot(data = county_census_map_state) +
    geom_sf(aes(fill = cases/population)) + 
    scale_fill_viridis_c(option = "magma", direction = -1) + 
    labs(title = paste(state_name),
         subtitle = "Cases per Capita after Second Wave") +
    theme_void() + 
    theme(text = element_text(family = "raleway", size = 25))

county_pax_deaths_w2 <- function(state_name) {

  county_census_map_state <- county_census_map_US_w2 %>% 
    filter(STATEFP == fips_code) %>% 
    filter(deaths >= 0)

  ggplot(data = county_census_map_state) +
      geom_sf(aes(fill = deaths/population)) + 
      scale_fill_viridis_c(option = "viridis", direction = -1) + 
      labs(title = paste(state_name),
           subtitle = "Deaths per Capita after Second Wave") +
      theme_void() + 
      theme(text = element_text(family = "raleway", size = 25))

county_state_map_w2 <- function(state_name) {

  county_map_state <- county_map_w2 %>% 
  filter(STATEFP == fips_code)

  ggplot(data = county_map_state) +
    geom_sf(aes(fill = cases)) + 
    scale_fill_viridis_c(option = "magma", direction = -1) + 
    labs(title = paste(state_name),
         subtitle = "After Second Wave") +
    theme_void()

# e.g. 
TX <- county_state_map("Texas")
CA <- county_state_map("California")
FL <- county_state_map("Florida")
MA <- county_state_map("Massachusetts")
NY <- county_state_map("New York")
NJ <- county_state_map("New Jersey")
IL <- county_state_map("Illinois")
GA <- county_state_map("Georgia")

# cases after second wave 
# e.g. 
TX_w2 <- county_state_map_w2("Texas")
CA_w2 <- county_state_map_w2("California")
FL_w2 <- county_state_map_w2("Florida")
MA_w2 <- county_state_map_w2("Massachusetts")
NY_w2 <- county_state_map_w2("New York")

NJ_w2 <- county_state_map_w2("New Jersey")
IL_w2 <- county_state_map_w2("Illinois")
GA_w2 <- county_state_map_w2("Georgia")

county_pax_w2

CA_pax_w2_cases <- county_pax_cases_w2("California")
CA_pax_w2_deaths <- county_pax_deaths_w2("California")

CA_3 <- county_pax_cases_w2("California")
CA_4 <- county_pax_deaths_w2("California")

NY_3 <- county_pax_cases_w2("New York")
NY_4 <- county_pax_deaths_w2("New York")

IL_3 <- county_pax_cases_w2("Illinois")
IL_4 <- county_pax_deaths_w2("Illinois")

FL_3 <- county_pax_cases_w2("Florida")
FL_4 <- county_pax_deaths_w2("Florida")

WI_3 <- county_pax_cases_w2("Wisconsin")
WI_4 <- county_pax_deaths_w2("Wisconsin")

ND_3 <- county_pax_cases_w2("North Dakota")
ND_4 <- county_pax_deaths_w2("North Dakota")

SD_3 <- county_pax_cases_w2("South Dakota")
SD_4 <- county_pax_deaths_w2("South Dakota")

GA_3 <- county_pax_cases_w2("Georgia")
GA_4 <- county_pax_deaths_w2("Georgia")

@@

plot_grid(TX, TX_w2, 
          CA, CA_w2, 
          FL, FL_w2, 
          IL, IL_w2, 
          MA, MA_w2, 
          NJ, NJ_w2, 
          NY, NY_w2, 
          ncol = 2)

plot_grid(FL_3, FL_4, 
          IL_3, IL_4, 
          ncol = 2)

plot_grid(NY_3, NY_4, 
          CA_3, CA_4,
          WI_3, WI_4,
          GA_3, GA_4,
          ncol = 2)

# ggsave("CA-comparison.png", plot_grid(CA, CA_msa), width = 8, height = 5, dpi = 300)
# ggsave("IL-comparison.png", plot_grid(IL, IL_msa), width = 8, height = 5, dpi = 300)
# ggsave("MA-comparison.png", plot_grid(MA, MA_msa), width = 8, height = 5, dpi = 300)
# 
# ggsave("CA-county-state.png", CA, width = 5, height = 6, dpi = 300)
# ggsave("IL-county-state.png", IL, width = 5, height = 6, dpi = 300)
# ggsave("MA-county-state.png", MA, width = 5, height = 6, dpi = 300)

# ggsave("county-state-waves.png", width = 8, height = 25, dpi = 300)

# ggsave("county-pax-w2_NY_CA_WI_GA.png", width = 14, height = 25, dpi = 300)
# 
# ggsave("county-pax-w2_FL_IL.png", width = 10, height = 8, dpi = 300)

@@

# ggsave("CA-metro-state.png", CA_msa, width = 5, height = 6, dpi = 300)
# ggsave("IL-metro-state.png", IL_msa, width = 5, height = 6, dpi = 300)
# ggsave("MA-metro-state.png", MA_msa, width = 5, height = 6, dpi = 300)
# ggsave("metro-state.png", width = 8, height = 5, dpi = 300)
```
### Metropolitan Cases
